Characterization of gaps in directly bonded Si compound optics

### 2014-04-01 AO_bondedSi.tex
add DTJ edits from page 5

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.95\columnwidth]{figs/SiBondTentCatFig.pdf}}
\caption{Schematic of a particle preventing bonding of two Si surfaces\label{figParticle}.  There are two conceivable scenarios in which particle contamination can cause gaps in the bond.  \emph{Left-} The particle serves as a mechanical structure hindering the Si-Si bond from zippering up.  The geometry is like a tent-pole.  \emph{Right-} The particle serves as a catalyst for gas formation.  There is evidence that hydrocarbons can serve as catalysts, the especially pernicious particles are ``thermally unstable hydrocarbon contaminants on the surfaces coming from plastic containers or simply from the ambient in a cleanroom.'' \cite{1998AnRMS..28..215G}. }
\end{figure}

Consider the following two conceivable pitfalls in Si-Si direct bonding.  The obvious pitfall is particle contamination.  Figure \ref{figParticle} shows a schematic of a particle wedged between two flat Si optical surfaces.  A single 0.6 $\mu$m particle can create a dark IR bubble from interference.  In the next section we show that smaller bubbles can unacceptably degrade the performance to as low as 10 nm.  In a class 100 cleanroom, the volume density could be as high as $\rho=100$ particles/ft$^3$, with sizes larger than 0.5 $\mu$m.  What we care about is not the volume number density of particles, but the delivered surface flux $F=\rho(D) v(D)$, where v(D) is the average freefall speed of particles, which is a function of particle size.  Figure 5 of Cooper 1986\cite{doi:10.1080/02786828608959094} shows the surface flux (particles cm$-2$ s$-1$) vs. particle size ($\mu$m).  For a change from 1 $\mu$m to 10$-2$ $\mu$m, there is an increase in a factor of $10^4$ in the particle flux expected.  In other words:
$$\log(F) = -2\log(D) + const.$$

So there will be roughly $10^4$ times more 10 nm sized particles than 1 $\mu$m sized particles, which means for every obviously detectable IR bubble, there are thousands more particles that could unacceptably degrade the transmission performance.  One key idea that saves the day, is the intuition that the areal fill factor scales at least as fast as $D^2$.  Imagine that the particles serve as miniature tentpoles.  The volume beneath the tentpole looks like a cone.  Since the number density goes down as roughly $D^-2$, (per the equation above) the total area covered by particles might be constant in $log(D)$.  Simply put, the big particles cover just as much area as the small particles, even though there are many more small particles.  It is further conceivable that the areal fill factor attributable to a tent pole particle scales even faster than $D^2$ since surface energy probably scales inversely with distance of the pieces (\`a la VanDerWaals).

It has been shown\cite{1992JEMat..21..669M} that the gases seep through the Si$-$Si interface, so pressure builds around those particles that serve as catalysts.  In this sense, the size of the particle causing an IR bubble cannot be uniquely identified from observations of the extent of IR bubble defects.  In section \ref{secResults} we address the question of the origin of the IR bubbles.  Specifically, are the particles more like \emph{tentpoles}, rigid structures that merely prevent the zippering up of the bond?  Or are the particles more like \emph{catalysts} so that their size is immaterial- the particles merely accelerate the production of gases that bow out the bond?  These are open questions.

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.95\columnwidth]{figs/SiTentCatFig2.pdf}}
\caption{Schematic of a particle preventing bonding of two Si surfaces\label{figParticle}.  There are two conceivable scenarios in which particle contamination can cause gaps in the bond.  \emph{Left-} The particle serves as a mechanical structure hindering the Si-Si bond from zippering up.  The geometry is like a tent-pole.  \emph{Right-} The particle serves as a catalyst for gas formation.  There is evidence that hydrocarbons can serve as catalysts.  The especially pernicious particles are ``thermally unstable hydrocarbon contaminants on the surfaces coming from plastic containers or simply from the ambient in a cleanroom'' \cite{1998AnRMS..28..215G}. }
\end{figure}

Consider the following two conceivable pitfalls in Si-Si direct bonding.  The obvious pitfall is particle contamination.  Figure \ref{figParticle} shows a schematic of a particle wedged between two flat Si optical surfaces.  A single 0.6 $\mu$m particle can create a dark IR bubble from interference.  In the next section we show that smaller bubbles can unacceptably degrade the performance to as low as 35 nm.  In a class 100 cleanroom, the volume density could be as high as $\rho=100$ particles/ft$^3$, with sizes larger than 0.5 $\mu$m.  What we care about is not the volume number density of particles, but the delivered surface flux $F=\rho(D) v(D)$, where $v(D)$ is the average freefall speed of particles, which is a function of particle size.  Figure 5 of Cooper 1986\cite{doi:10.1080/02786828608959094} shows the surface flux (particles cm$^{-2}$ s$^{-1}$) vs. particle size ($\mu$m).  For a change from 1 $\mu$m to 10$^{-2}$ $\mu$m, there is an increase in a factor of $10^4$ in the particle flux expected.  In other words:
$$\log(F) = -2\log(D) + const.$$

So there will be roughly $10^4$ times more 10 nm sized particles than 1 $\mu$m sized particles.  For every obviously detectable IR bubble, there are thousands more particles that could unacceptably degrade the transmission performance.  One key idea that saves the day, is the intuition that the areal fill factor scales at least as fast as $D^2$.  Imagine that the particles serve as miniature tentpoles.  The volume beneath the tentpole looks like a cone.  Since the number density goes down as roughly $D^{-2}$, (per the equation above) the total area covered by particles might be constant in $log(D)$.  Simply put, the big particles cover just as much area as the small particles, even though there are many more small particles.  It is further conceivable that the areal fill factor attributable to a tent pole particle scales even faster than $D^2$ since surface energy probably scales inversely with distance of the pieces (\`a la VanDerWaals).

It has been shown\cite{1992JEMat..21..669M} that the gases seep through the Si$-$Si interface.  Pressure builds around catalysts.  In this sense, the size of the particle causing a gap cannot be uniquely identified from observations of the extent of gaps.  In section \ref{secResults} we address the question of the origin of the IR bubbles.  Specifically, are the particles more like \emph{tentpoles}, rigid structures that merely prevent the zippering up of the bond?  Or are the particles more like \emph{catalysts} so that their size is immaterial- the particles merely accelerate the production of gases that bow out the bond?  These are open questions.
